\newcommand{\stcomp}[1]{\bar{#1}}

# Homeworks


## Homework 2

[Invitation link: https://classroom.github.com/g/qogtEQ5b](https://classroom.github.com/g/qogtEQ5b)

**Disclaimer**: As in the previous homework, please note that the dataset used here is simplified for _ease of use_ and the analysis here
MUST be viewed an an exercise, not real-world research! For the full dataset always refer to the data source!

The dataset `linton` is an adapted version from of the data used to study the incubation period of SARS-Cov-19, the virus that causes COVID19 @Linton2020. It contains 114 observations on COVID19 patients, mainly from mainland China. For this homework we are only interested in the `Incubation` variable in the dataset
that contains the time in days from exposure to the virus to symptoms onset.

1. Read and download the data (already done in the starter code)

2. Let $y_i$ denote the incubation time for patient $i = 1,\ldots,n$. Let $u_i \sim N(0, \sigma ^ 2)$ be a normally distributed random variable with zero mean and variance $\sigma ^ 2$. Furthermore, assume that the error terms $u_i$ are independent. Fit the linear regression model:

\begin{align}
  y_i = \beta_0 + u_i, \quad i = 1,\ldots,n. (\#eq:hw1-regression-model)
\end{align}

_Hint_: use the `lm` function in R.

```{r, eval=FALSE}
  fit <- lm(Incubation ~ 1, data = linton) ## This instructs lm to use only a constant
```

2. Print the summary of the regression fit

```{r, eval=FALSE}
  summary(fit)
```

3. Write down the estimated regression equation (as a comment in the code).

4. What is the meaning of the intercept $\beta_0$ in the model (write your answer as a comment in the code)?

5. Estimate a 95 percent confidence interval for $\beta_0$.

6. Given the hypothesis:

\begin{align}
  H_0: \beta_0 = 8 (\#eq:hw2-null-hypothesis)\\
  H_1: \beta_0 \neq 8 (\#eq:hw2-alternative-hypothesis)
\end{align}

  - Explain the meaning of \@ref(eq:hw2-null-hypothesis) in plain language.
  - Using the regression output, test the hypothesis at a 5 percent significance level and write down your decision to
    reject or not to reject the null hypothesis.
    
7. Using the regression output, estimate the probability that a randomly chosen person will have an incubation period
  between 5 and 10 days.

8. Do you see any problems with the choice of the statistical model in \@ref(eq:hw1-regression-model) (write down your answer as a comment in the code)?

